Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
updated maps

|-----|--------------------------------------------------------|---------------------------------------------------------|-----------------|

@@

### A sample of ready-to-process data
```{r a sample of data }
#| warning: false
#| message: false
```

### PCA Summary
```{r Map}
#| warning: false
#| message: false
```

### K-means cluster
```{r K-means cluster}
#| warning: false
#| message: false
```
:::

@@

::: {.panel-tabset style="font-size:16px"}
### Map
```{r Map}
#| warning: false
#| message: false
library(plotly)
library(leaflet)
library(sf)
library(dplyr)

@@

-   Heavily reliant on food supplies from other regions.

:::

@@

|-----|-------------------------------|-----------------------------------------------------------|------------------------------------------------------------------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|--------------|-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------------------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |

>>>>

|-----------------|-----------------------|-----------------|-----------------|

@@

### A sample of ready-to-process data

```{r a sample of data }
#| warning: false
#| message: false
library(gt)
readr::read_csv("data/sample_input.csv") |> 
  gt()|>
  tab_header(
    title = "A sample of the Data"
  )|>
  cols_label(
    idkec_dum = "ID",
    nmkab = "District",
    nmkec = "Sub-district",
    distance_to_plantation = "Dist. to Plantation (m)",
    distance_to_road = "Dist. to Road (m)",
    distance_to_commodity_processing_factory = "Dist. to Comm.Proc Factory (m)"
  )|>
  fmt_number(
    columns = c(distance_to_plantation, distance_to_road, distance_to_commodity_processing_factory),
    decimals = 2
  )
```

### PCA Summary

```{r Map}
#| warning: false
#| message: false
```

### K-means cluster

```{r K-means cluster}
#| warning: false
#| message: false
```
:::

@@

```{r Map}
#| warning: false
#| message: false
library(plotly)
library(leaflet)
library(sf)
library(dplyr)

@@

-   Heavily reliant on food supplies from other regions.
:::

@@

|------------------|------------------|------------------|-------------------|
>>>>>>> Stashed changes

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|------------------|------------------|------------------|-------------------|
>>>>>>> Stashed changes
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
